SunPy - Python for Solar Physics

### 2014-01-19 2-1-Map.tex

\begin{listing}
\begin{minted}{python}

\begin{listing}
\begin{minted}{pycon}

@@

@@

>>>>

\begin{listing}[h]
\begin{minted}{pycon}

@@

\begin{listing}[h]
\begin{minted}{python}

@@

\begin{listing}[h]
\begin{minted}{python}
import matplotlib.pyplot as plt
import sunpy.map

#Create a composite map from two files
compmap = sunpy.map.Map('aia_1600_image.fits', 'RHESSI_image.fits', 
composite=True)

#Set the RHESSI image (index 1) to have contour levels and a red colour map.
compmap.set_levels(1,range(0,50,5),percent=True)
compmap.set_colors(1,'Reds_r')

#Plot the result and crop
ax = plt.subplot()
compmap.plot()
ax.axis([200,600,-600,-200])
\end{minted}
\includegraphics[width=0.8\columnwidth]{comp_map_example}
\caption{Example demonstrating a CompositeMap plot, using contours and how 
SunPy integrates with matplotlib's pyplot functional interface.}
\label{code:compmap_1}
\end{listing}

\begin{listing}[h]
\begin{minted}{python}
import sunpy.map

compmap = sunpy.map.Map('aia_lev1_171a_2014_01*fits', cube=True)
compmap.peek()
\end{minted}
\includegraphics[width=0.8\columnwidth]{aia_cube_controls}
\caption{An example showing creation of a MapCube from a glob file search. The 
resultant plot makes use of matplotlib's interactive widgets to allow scrolling 
through the MapCube.}
\label{code:mapcube_1}
\end{listing}

\begin{listing}[h]
\begin{minted}{python}
import sunpy.map
from matplotlib import animation

mapc = sunpy.map.Map('aia_lev1_171a_2014_01*fits', cube=True)
anim = mapc.plot()
Writer = animation.writers['ffmpeg']
writer = Writer(fps=10, metadata=dict(artist='SunPy'), bitrate=1800)
anim.save('aia_cube.ogv')
\end{minted}
\caption{Example showing how to save a video animation from a MapCube, using 
matplotlib's animation framework.}
\label{code:mapcube_2}
\end{listing}
